---
title: "Candidate Event Tracker"
resource_files:
- .httr-oauth
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(googlesheets)
library(kableExtra)
library(leaflet)
# library(ggmap)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
options(tigris_class = "sf")



### DATA LOADING AND PREP

# import data from Google Sheet 

#register DW's 2020 google sheet using stored sheet id key 
mykey <- Sys.getenv("DW2020_KEY")
dw2020 <- gs_key(mykey)

#read in all the data in the rally/event tab
events <- dw2020 %>% 
  gs_read(ws = "AK VER Rally / Event Tracker") %>% 
  clean_names() 

#set formatting of certain columns
events <- events %>% 
  mutate(
    date = mdy(date),
    thru_date = mdy(thru_date),
    cand_fullname = as.factor(cand_fullname),
    state = as.factor(state),
    cd_if_known = as.factor(cd_if_known),
    event_type = as.factor(event_type),
    cand_fullname = as.factor(cand_fullname),
    cand_lastname = as.factor(cand_lastname),
    sponsor = as.factor(sponsor)
         )

saveRDS(events, "events_saved.rds")

#by state counts - only PAST events
bystate <- events %>% 
  filter(date < Sys.Date()) %>% 
  count(state) %>% 
  arrange(desc(n)) %>% 
  head(10)
#reorder factors to order bars descending
bystate <- bystate %>% 
  mutate(
    state = as.factor(state),
    state = fct_reorder(state, desc(n))
    )


# by cand_fullname counts to date - only PAST events
bycand <- events %>%
  filter(date < Sys.Date()) %>%  
  count(cand_fullname) %>%
  arrange(desc(n)) %>% 
  head(10)
#reorder factors to order bars descending
bycand <- bycand %>%
  mutate(
    cand_fullname = as.factor(cand_fullname),
    cand_fullname = fct_reorder(cand_fullname, desc(n))
    )


#slimmed version of table for display in summary tab
events_selectcols <- events %>% 
  select(cand_fullname, 
         date, 
         # thru_date,
         city, 
         state, 
         addtl_cities, 
         event_type, 
         sponsor, 
         description)



# INTERVIEWS/REMARKS DATA #####
# 
# keyremarks <- dw2020 %>%
#   gs_read(ws = "Key Interviews/Remarks") %>%
#   clean_names()
# 
# keyremarks <- keyremarks %>% 
#   mutate(
#     date = dmy(date),
#     candidate = as.factor(candidate),
#     venue = as.factor(venue),
#     subject_1 = as.factor(subject_1),
#     subject_2 = as.factor(subject_2),
#     state = as.factor(state),
#     on_cam = as.factor(on_cam)
#   )

### CANDIDATE ANNOUNCEMENTS DATA ####
announcements <- dw2020 %>%
  gs_read(ws = "Candidate Announcements") %>%
  clean_names() %>% 
  mutate(
    date = mdy(date)
  ) %>% 
  select(-x7, -x8) %>% 
  arrange(desc(date))

announcements$date <- format(announcements$date, "%m/%d/%Y")


### GEOGRAPHIC DATA ####

# # Downloading the shapefiles for states at the lowest resolution from tigris
# states <- states(cb=T)
# #save result
# saveRDS(states, "states_saved.rds")

## use saved version to pull states from to save processing time (comment out code above when doing so)
states <- readRDS("states_saved.rds")



# write_csv(events, "events_temp.csv")
# write_csv(bystate, "bystate.csv")

# set time object set to EST
d <- Sys.Date()
# d <- .POSIXct(d, "EST")
  
t <- Sys.time()
t <- .POSIXct(t, "EST")

```


Summary Charts and Table
===================================== 
Trips from Nov 06 through `r format(d, format="%b %d")`. To filter, click on the boxes above the columns. To sort, use the up/down arrows by the column names. *Note: if a candidate visits multiple cities in the same state, on the same campaign swing, they are counted below as one campaign trip. The additional locations are included in the "addtl_cities" column.*  (Last updated on `r format(t, format="%B %d %I:%M %p %Z")`) 
<!-- (This dashboard was last updated at `r format(Sys.time(), "%a %b %d %X")`)  -->

Row {data-height=650}
-----------------------------------------------------------------------

### {data-width=800}

```{r}

#filter only past events

events_past <- events_selectcols %>%
  filter(date <= today("EST"))

datatable(events_past, 
          rownames = FALSE, 
          filter = "top",
          options = list(searchHighlight = TRUE)) %>% 
  formatDate('date', 'toDateString') %>%  
  # formatDate('thru_date', 'toDateString') %>%
  formatStyle('cand_fullname', fontWeight = 'bold') 





```


### How many trips a candidate's taken to each state {data-width=200}

```{r}

#filter only past events

events_past_grp <- events_selectcols %>%
  filter(date <= today("EST")) %>% 
  count(cand_fullname, state) %>% 
  arrange(cand_fullname, desc(n)) %>% 
  rename(trips = n)

datatable(events_past_grp, 
          rownames = FALSE, 
          # filter = "top",
          options = list(bPaginate = FALSE, 
                         searching = FALSE
    #                      initComplete = JS(
    # "function(settings, json) {",
    # "$(this.api().table().header()).css({'background-color': '#EE82EE', 'color': '#fff'});",
    # "}")
                         )
          )



```


Row {data-height=350}
-----------------------------------------------------------------------

### Top states for trips since midterm election

```{r}


d <- ggplot(data = bystate, aes(x = state, y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#ffb3ba") + 
  # coord_flip() + 
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2) 

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu
  


```


### Candidates with most trips since midterm election

```{r}



d <- ggplot(data = bycand, aes(x = cand_fullname, y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#FFC966") +
  # coord_flip() +
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2)

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu


```





Upcoming Events Breakdown
=====================================


Row {data-height=300}
-----------------------------------------------------------------------

### Next trip happening

```{r}

t <- events %>%
  filter(date > today("EST"))

next_date <- min(t$date)


day <- as.character(day(next_date))
month <- as.character(month(next_date))

h_desc <- glue("{month}/{day}")

valueBox(h_desc, icon = "fa-pencil", color = "#E76F61")


```

### Total trips since midterms

```{r}

### figure out which hearing is next?
tot <- events %>%
  filter(date < today("EST")) %>%
  nrow()

valueBox(tot, icon = "fa-step-backward", color = "#F3B279")


```

### Total scheduled trips ahead

```{r}

### figure out which hearing is next?
tot_ahead <- events %>%
  filter(date > today("EST")) %>%
  nrow()

valueBox(tot_ahead, icon = "fa-plane", color = "#48B052")


```


Row {data-height=700}
-----------------------------------------------------------------------

### Trips coming up over the next week

```{r}

next5 <- events %>% 
  filter(date > Sys.Date(),
         date < (Sys.Date()+7)) %>% 
  mutate(location = paste0(city, ", ", state)) %>% 
  select(cand_lastname, date, location, addtl_cities, event_type, description) %>% 
  arrange(date)

#remove NA's from city descriptions without a city
next5$location <- str_remove(next5$location, "NA, ")

next5$date <- format(next5$date, "%m/%d/%Y")

next5 %>% 
    kable() %>% 
    kable_styling(bootstrap_options = c("striped"), 
                full_width = F,
                position = "left")


```


### Trips per state over the next week

```{r}

#### STATE BY STATE SHADED MAP ####

upcoming_states <- events %>% 
  filter(date > Sys.Date(),
         date < (Sys.Date()+7)) %>% 
  group_by(state) %>%
  summarize(total=n()) 

# Now we use the Tigris function geo_join to bring together 
# are the two columns they'll be joined by
states_merged_sb <- geo_join(states, upcoming_states, "STUSPS", "state")

# Creating a color palette based on the number range in the total column
pal <- colorNumeric("YlGn", domain=states_merged_sb$total)

# Getting rid of rows with NA values
# Using the Base R method of filtering subset() because we're dealing with a SpatialPolygonsDataFrame and not a normal data frame, thus filter() wouldn't work
states_merged_sb <- subset(states_merged_sb, !is.na(total))
states_merged_sb$total <- as.integer(states_merged_sb$total)

#create map with hover popups

popup_sb <- paste0("Trips over coming week: ", as.character(states_merged_sb$total))

leaflet() %>%
  addTiles() %>%
  # setView(-98.483330, 38.712046, zoom = 4) %>% 
  addPolygons(data = states_merged_sb , 
              fillColor = ~pal(states_merged_sb$total), 
              fillOpacity = 0.9, 
              weight = 0.2, 
              smoothFactor = 0.2,
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE),
              label=popup_sb,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = pal, 
            values = states_merged_sb$total,
            bins = 4,
            position = "bottomright", 
            title = "Total trips", 
            labFormat = labelFormat(digits = 0)
            )

# 
# mymap %>% 
#   addTiles()



```





Detailed Event Data 
=====================================
To filter, click on the boxes at the top of the columns. To sort, use the up/down arrows by the column names.

Row {data-height=1000}
-----------------------------------------------------------------------

```{r}

ev_big <- events %>% 
  select(-cand_restname, -cand_lastname, -cd_if_known, -county) %>% 
  mutate(
    approx_date = as.factor(approx_date),
    city = as.factor(city)
    )

datatable(ev_big,
          rownames = FALSE,
          filter = "top",
          extensions = 'Buttons',
          options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip',
     buttons = c('copy', 'excel', 'pdf', 'print')
          )) %>%
  formatDate('date', 'toLocaleDateString') %>%
  formatDate('thru_date', 'toLocaleDateString') %>%
  formatStyle('cand_fullname', fontWeight = 'bold')


```





Maps: State by State
=====================================
Maps

Row 
-----------------------------------------------------------------------

### Total trips to date by all candidates

```{r}

#### STATE BY STATE SHADED MAP ####

upcoming_states <- events %>% 
  filter(date <= Sys.Date()) %>% 
  group_by(state) %>%
  summarize(total=n()) 

# Now we use the Tigris function geo_join to bring together 
# are the two columns they'll be joined by
states_merged_sb <- geo_join(states, upcoming_states, "STUSPS", "state")

# Creating a color palette based on the number range in the total column
pal <- colorNumeric("YlOrRd", domain=states_merged_sb$total)

# Getting rid of rows with NA values
# Using the Base R method of filtering subset() because we're dealing with a SpatialPolygonsDataFrame and not a normal data frame, thus filter() wouldn't work
states_merged_sb <- subset(states_merged_sb, !is.na(total))
states_merged_sb$total <- as.integer(states_merged_sb$total)

#create map with hover popups

popup_sb <- paste0("Trips: ", as.character(states_merged_sb$total))

leaflet() %>%
  addTiles() %>%
  # setView(-98.483330, 38.712046, zoom = 4) %>% 
  addPolygons(data = states_merged_sb , 
              fillColor = ~pal(states_merged_sb$total), 
              fillOpacity = 0.9, 
              weight = 0.2, 
              smoothFactor = 0.2,
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE),
              label=popup_sb,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = pal, 
            values = states_merged_sb$total,
            # bins = 4,
            position = "bottomright", 
            title = "Total trips", 
            labFormat = labelFormat(digits = 0)
            )



```


### All known upcoming trips (subject to change)

```{r}

#### STATE BY STATE SHADED MAP ####

upcoming_states <- events %>% 
  filter(date > Sys.Date()) %>% 
  group_by(state) %>%
  summarize(total=n()) 

# Now we use the Tigris function geo_join to bring together 
# are the two columns they'll be joined by
states_merged_sb <- geo_join(states, upcoming_states, "STUSPS", "state")

# Creating a color palette based on the number range in the total column
pal <- colorNumeric("YlGn", domain=states_merged_sb$total)

# Getting rid of rows with NA values
# Using the Base R method of filtering subset() because we're dealing with a SpatialPolygonsDataFrame and not a normal data frame, thus filter() wouldn't work
states_merged_sb <- subset(states_merged_sb, !is.na(total))
states_merged_sb$total <- as.integer(states_merged_sb$total)

#create map with hover popups

popup_sb <- paste0("Upcoming trips: ", as.character(states_merged_sb$total))

leaflet() %>%
  addTiles() %>%
  # setView(-98.483330, 38.712046, zoom = 4) %>% 
  addPolygons(data = states_merged_sb , 
              fillColor = ~pal(states_merged_sb$total), 
              fillOpacity = 0.9, 
              weight = 0.2, 
              smoothFactor = 0.2,
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE),
              label=popup_sb,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = pal, 
            values = states_merged_sb$total,
            # bins = 4,
            position = "bottomright", 
            title = "Total trips", 
            labFormat = labelFormat(digits = 0)
            )



```

Row 
-----------------------------------------------------------------------

### Total trips since midterms

```{r}

### figure out which hearing is next?
tot <- events %>%
  filter(date < today("EST")) %>%
  nrow()

valueBox(tot, icon = "fa-step-backward", color = "#F3B279")


```

### Total scheduled trips ahead

```{r}

### figure out which hearing is next?
tot_ahead <- events %>%
  filter(date > today("EST")) %>%
  nrow()

valueBox(tot_ahead, icon = "fa-plane", color = "#48B052")


```





<!-- Key SOTs & Remarks  -->
<!-- ===================================== -->
<!-- To filter, click on the boxes above the column names. To sort, use the up/down arrows by the column names. -->

<!-- Row {data-height=1000} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ```{r} -->

<!-- remarks_big <- keyremarks %>%  -->
<!--   select(candidate, -->
<!--          date, -->
<!--          venue, -->
<!--          city, -->
<!--          state, -->
<!--          on_cam, -->
<!--          ms_number, -->
<!--          subject_1, -->
<!--          tc_in, -->
<!--          key_sound, -->
<!--          subject_2, -->
<!--          tc_in_2, -->
<!--          other_sound, -->
<!--         source_link -->
<!--           ) %>%  -->
<!--   mutate( -->
<!--     on_cam = as.factor(str_to_lower(on_cam)) -->
<!--   ) %>%  -->
<!--   arrange(desc(date)) -->

<!-- datatable(remarks_big, -->
<!--           rownames = FALSE, -->
<!--           filter = "top", -->
<!--           extensions = 'Buttons', -->
<!--           options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip', scrollX=TRUE,scrollY=400,  -->
<!--      buttons = c('copy', 'excel', 'pdf', 'print') -->
<!--           )) %>% -->
<!--   formatDate('date', 'toLocaleDateString') %>% -->
<!--   formatStyle('candidate', fontWeight = 'bold') -->



<!-- ``` -->




Candidate Announcements 
=====================================

Row 
-----------------------------------------------------------------------

```{r}

announcements %>% 
    kable() %>% 
    kable_styling(bootstrap_options = c("striped", "condensed"), 
                full_width = F,
                position = "left")


```


Questions?
=====================================

Row 
-----------------------------------------------------------------------
If you have any questions about this candidate tracker, please give a shout to David Wright or Aaron Kessler in the DC bureau at David.E.Wright@turner.com or Aaron.Kessler@turner.com.  Thanks!
